Statistical Inference for inter-arrival times of extreme events in bursty time series

### 2018-12-09 article_springer/article_springer.Rmd
introduce theorem environment

preamble: | 
  \usepackage{amssymb}
  \usepackage{natbib}
  \newtheorem{definition}{Definition}

@@

**Theorem:**

: Let the waiting times $J_k$ be in the domain of attraction of a positively skewed sum-stable law with stability parameter $0 < \beta < 1$; more precisely,
\begin{align} \label{eq:stability}
\frac{W_1 + \ldots + W_n}{b(n)} \overset{d}{\longrightarrow} D, 
\quad n \to \infty
\end{align}
for a function $b(n)$ which is regularly varying at $\infty$ with parameter $1/\beta$, and where $\mathbf E[\exp(-sD)] = \exp(-s^\beta)$. Write $p := \mathbf P(J > \ell)$. Then the weak convergence
$$
\frac{T(\ell)} {b(1/p)} \to W_\beta \quad \text{ as } \quad \ell \uparrow x_R
$$  
holds, where the Mittag-Leffler random variable $W_\beta$ is defined on 
the positive real numbers via 
$$
\mathbf E[\exp(-sW_\beta)] = \frac{1}{1+s^\beta}.
$$

>>>>

preamble: | 
  \usepackage{amssymb}
  \usepackage{natbib}
  \newtheorem{definition}{Definition}
  \newtheorem{theorem}{Theorem}

@@

\begin{theorem}
Let the waiting times $J_k$ be in the domain of attraction of a positively skewed sum-stable law with stability parameter $0 < \beta < 1$; more precisely,
\begin{align} \label{eq:stability}
\frac{W_1 + \ldots + W_n}{b(n)} \overset{d}{\longrightarrow} D, 
\quad n \to \infty
\end{align}
for a function $b(n)$ which is regularly varying at $\infty$ with parameter $1/\beta$, and where $\mathbf E[\exp(-sD)] = \exp(-s^\beta)$. Write $p := \mathbf P(J > \ell)$. Then the weak convergence
$$
\frac{T(\ell)} {b(1/p)} \to W_\beta \quad \text{ as } \quad \ell \uparrow x_R
$$  
holds, where the Mittag-Leffler random variable $W_\beta$ is defined on 
the positive real numbers via 
$$
\mathbf E[\exp(-sW_\beta)] = \frac{1}{1+s^\beta}.
$$ 
\end{theorem}
